### 2019-08-23 thesis.tex
Final (I guess)

In the context of plasma kinetic theory, processes involving waves
and kinetic instabilities, the so-called \emph{collective processes},
are almost exclusively associated with situations in which the effects
of collisional dissipation can be neglected, what happens when the
studied phenomenon evolves in a much shorter time-scale than the
collisional relaxation time of the plasma in question \cite{akhi1967}.
In such cases, the plasma dynamics may be described by the Vlasov-Maxwell
system, a complex set of coupled equations which solution invariably will
depend on some degree of approximation. In the presence of small
amplitude oscillations in a fully ionized plasma, we can make use
of perturbation theory in order to solve such complicated system
\cite{klimo}. From this method, one may obtain simpler approximations
like the linear theory and the quasilinear formalism, and also
more complex formulations, like the weak turbulence theory, which
takes into account low-order nonlinearities on the plasma dynamics.

@@

In the quasilinear theory, low-order nonlinear terms are kept in
the equation for the time evolution of the velocity distribution
function. The velocity distribution will then evolve in time through
a process of diffusion in velocity space, in which the diffusion
coefficient depends on the spectral energy density of the waves.
The dispersion relation is formally given by the same expression
obtained under the linear theory, except that now it depends on a
time-dependent velocity distribution function, which must vary in a
much slower time-scale than the period of the plasma oscillations.
Under such condition, the gradual changing on the velocity space
shape slowly modifies the wave spectrum, which new form will then
alter the velocity distribution function and so on, until a new
quasi-stationary equilibrium state is attained \cite{gurnett2017}.
However, depending on the phenomenon being described this saturation
state reached under the quasilinear approximation might keep on
evolving if higher order nonlinearities are taken into account
\cite{akhi2}. This kind of nonlinear analysis is given by the
\emph{weak turbulence theory}, which is the next step in this chain
of perturbative approximations.

@@

The main subject of this thesis is discussed in \Cref{noneigenmode}. In
\Cref{sec:inc-non} we show the methodology used in the formulation of this
new generalization and the outcome of its inclusion in the quasilinear
wave equation, and in the particle kinetic equation. \Cref{sec:non-non}
describes the inclusion of the noneigenmode fluctuations in the nonlinear
wave equations and the resulting terms, which are the main concern of
the present analysis. In \Cref{main}, we contextualize the present work
regarding the theory discussed in the previous chapter and present the
results obtained in appended papers. \Cref{cha:final}, summarizes the
results and presents a brief discussion on the and perspectives of this
new generalized formalism, and its relevance for the next generation of
solar physics research.

@@

On the left-hand side of  Eq. \eqref{eq-cin-par} we have retained the
slow adiabatic derivative $i(\partial/\partial t)$. To deal with
that we employ two-step approximation \cite{Yoon00} and redefine
the angular frequency $\omega \rightarrow \omega+i \partial/\partial t$.
Then the equation for the
% LFZ180216: "the perturbed"?
% Sabrina: OK
perturbed distribution may be iteratively
solved up to third order in electric field.  The solution is then
inserted into Eq. \eqref{poisson-flut}
% the perturbed Poisson equation
% LFZ180216: Se o nome Poisson foi mudado anteriormente, deve ser mudado aqui
% também.
% Sabrina: coloquei o número da equação no lugar. Pode ser?
% LFZ180220: OK
and,  under the assumption that there are random phases associated with
the fluctuations, we take the appropriated ensembles averages. This
procedure results in the nonlinear spectral balance equation. At this
point, according to the two-time approximation, the slow time derivative
is reintroduced \cite{YZKS16}. This procedure results in the nonlinear
spectral balance equation\footnote{Equation \eqref{nlebe} is not in the
  same form that appears in Refs. \cite{Yoon00,Tigik2015}. The reason
  for this choice (see Eq. 2.59 of Ref. \cite{YZKS16}), will become
  clear in the next chapter.}
\begin{eqnarray}
  &&\frac{i}{2}\frac{\partial \epsilon({\bf k},\omega)}{\partial \omega}
  \frac{\partial \left<\delta E^2\right>_{{\bf k},\omega}}{\partial t}
  +\mbox{Re}\,\epsilon({\bf k},\omega)\left<\delta E^2 \right>_{{\bf k},\omega}
+i\mbox{Im}\,\epsilon({\bf k},\omega)\left<\delta E^2 \right>_{{\bf k},\omega}
  \nonumber\\
  &&\qquad \qquad \qquad -\frac{2}{\pi}\frac{1}{k^2\epsilon^*({\bf k},\omega)}
     \sum_ae_a^2\int d{\bf v}\,\delta(\omega-{\bf k\cdot v})F_a({\bf v})
  \nonumber\\
  &&=-2\int d{\bf k'} \int d\omega '\
  \biggl\{ \left[\chi^{(2)}({\bf k'},\omega '|{\bf k-k'},
    \omega-\omega ')\right]^2
  \biggl[\frac{\left<\delta E^2\right>_{{\bf k-k'},\omega-\omega '}}
       {\epsilon({\bf k'},\omega ')}
  \nonumber\\
  &&+\frac{\left<\delta E^2\right>_{{\bf k'},\omega '}}
  {\epsilon({\bf k-k'},\omega-\omega ')}\biggr]
     -\bar \chi^{(3)}({\bf k'},\omega|-{\bf k'},-\omega '|{\bf k},\omega)
      \left<\delta E^2\right>_{{\bf k'},\omega'}\biggr\}
  \left<\delta E^2\right>_{{\bf k},\omega}\nonumber\\
  &&+2\int d{\bf k'} \int d\omega '
  \frac{|\chi^{(2)}({\bf k'},\omega '|{\bf k-k'},\omega-\omega ')|^2}
{\epsilon^*({\bf k},\omega)}
\left<\delta E^2\right>_{{\bf k'},\omega '}
     \left<\delta E^2\right>_{{\bf k-k'},\omega-\omega '}
  \label{nlebe}\\
&&-\frac{4}{\pi}\int d{\bf k '} \int d\omega '\
\frac{1}{k^2|\epsilon({\bf k'},\omega ')|^2}
\biggl[ \frac{[\chi^{(2)}({\bf k'},\omega '|{\bf k-k'},\omega-\omega ')]^2}
{\epsilon({\bf k-k'},\omega-\omega ')}
    \left<\delta E^2 \right>_{{\bf k},\omega}
  \nonumber\\
&&-\frac{|\chi^{(2)}({\bf k'},\omega '|{\bf k-k'},\omega-\omega ')|^2}
{\epsilon^*({\bf k},\omega)}
\left<\delta E^2 \right>_{{\bf k-k'},\omega-\omega '}\biggr]
\sum_ae_a^2\int d{\bf v}\, \delta(\omega '-{\bf k \cdot v})F_a({\bf v})
  \nonumber\\
&&-\frac{4}{\pi}\int d{\bf k '} \int d\omega '\
\frac{1}{|{\bf k - k'}|^2|\epsilon({\bf k-k'},\omega-\omega ')^2}
\biggl[ \frac{[\chi^{(2)}({\bf k'},\omega '|{\bf k-k'},\omega-\omega ')]^2}
{\epsilon({\bf k'},\omega ')}\left<\delta E^2 \right>_{{\bf k},\omega}
  \nonumber\\
&&-\frac{|\chi^{(2)}({\bf k'},\omega '|{\bf k-k'},\omega-\omega ')|^2}
{\epsilon^*({\bf k},\omega)}
\left<\delta E^2 \right>_{{\bf k'},\omega '}\biggr]
\sum_ae_a^2\int d{\bf v}\, \delta(\omega-\omega '-{\bf (k-k')\cdot v})F_a({\bf v})
\nonumber
\end{eqnarray}
where on the left-hand side we have the expressions that correspond
to the linear equation and on the right-hand side are the nonlinear
expressions. The term
\begin{equation} 
\epsilon({\bf k},\omega)=1+\sum_a\chi_a({\bf k},\omega)
\end{equation}
is the linear dielectric response function.

@@

Equation \eqref{nlebe} is a general expression. The usual
approach in plasma kinetic theory is to assume $|\mbox{Im}\
\epsilon({\bf k},\omega)|\ll|\mbox{Re}\ \epsilon({\bf k},\omega)|$.
Then, the imaginary part of \eqref{nlebe} leads to the wave kinetic
equation, while the real part leads to the wave dispersion equation,
which solutions are the wave dispersion relations.

@@

The following approximations and definitions were used to write
the above equations
\begin{displaymath}
\frac{1}{\epsilon '_\parallel({\bf k},\sigma\omega_{\bf k}^L)}
=\frac{\sigma\mu_{\bf k}^L\,\omega_{\bf k}^L}{2},\qquad
\frac{1}{\epsilon '_\parallel({\bf k},\sigma\omega_{\bf k}^S)}
=\frac{\sigma\mu_{\bf k}^S\,\omega_{\bf k}^L}{2},\qquad
\end{displaymath}
\begin{displaymath}
\mu_{\bf k}^L=1,\qquad
\mu_{\bf k}^S=|k|^3\lambda_{De}^3\biggl(\frac{m_e}{m_i}\biggr)^{1/2}
\biggl(1+\frac{3T_i}{T_e}\biggr)^{1/2},
\end{displaymath}

\chapter{Weak turbulence for collisional plasmas}
\label{noneigenmode}
In \Cref{cha:weak-turb} we made a brief review of the standard weak
turbulence theory procedure. Such procedure takes into account only
the contributions from the linear eigenmodes. The basic premise of this
conventional approach claims that only frequencies $\omega=\omega_{\bf k}$
that satisfy the dispersion relations are considered significant, even if
the general electrostatic fluctuations $\left<\delta E^2\right>_{{\bf k},\omega}$
are characterized by all ${\bf k}$ and $\omega$. Therefore, the fluctuations
which $\omega \ne \omega_{\bf k}$, which characterize the noneigenmodes,
are ignored. In Ref. \cite{YZKS16} the authors present a generalization
of this customary approach, where, besides the traditional inclusion of
the normal modes, it is also taken into account the contribution from the
noneigenmode fluctuations. The result is a generalized expression for the
spectral energy density of the waves, with some remarkable consequences
for the wave and particle kinetic equations.

The generalized spectral energy density, which contains the noneigenmode
contribution, is the central factor of this new kinetic turbulence theory
for collisional plasmas. When it is substituted in the nonlinear terms of
the nonlinear spectral balance equation, three new terms appear in the wave
kinetic equation. The first expression is an extension for the spontaneous
scattering equation. The second term is a new, rigorous expression for the
collisional damping rate of plasma waves. The third equation depicts a
hitherto unknown process of electrostatic radiation emission, in the eigenmode
frequency range, due to particle scattering. This underlying electrostatic
form of braking radiation was then called \emph{electrostatic bremsstrahlung}
\cite{YZKS16}. For the particle kinetic equation, the application of this
generalized expression is responsible for the arising of the Balescu-Lenard
collision integral, without any \emph{ad hoc} addition.

@@

\section{Noneigenmode contribution to nonlinear wave
  kinetic equation}
\label{sec:non-non}
For the nonlinear wave kinetic equation, the implementation is far more
extensive and complicated than the two previous cases. In this text, we
provide a brief explanation of the method, which is not very different
from the quasilinear case, though it is way more complex, and present some
critical remarks regarding the inclusion of noneigenmodes in the nonlinear
wave equation. It is worth to mention again, that a more detailed procedure
of the inclusion of the noneigenmode contribution in the weak turbulence's
equations can be seen in \cite{YZKS16}.

@@

\chapter{Weakly turbulent processes in the presence of
  collisional interactions}
\label{main}
The generalization introduced in \cite{YZKS16} and summarized in
\Cref{noneigenmode}, is an innovative approach, in which the contribution
of the usually neglected noneigenmode fluctuations is taken into account
along with the well-known eigenmodes contribution. The outcome of this new
formulation is a first principles theory that combines both collective
and non-collective processes, assuming the propagation of electrostatic
oscillations in unmagnetized plasmas, without any \emph{ad hoc} addition.
Such theory is the basis of the present research, which primary objective
is performing numerical analysis of the generalized weak turbulence equations,
and then investigate its applications on the description and interpretation
of space plasma phenomena. More specifically, the solar plasma, where the
results of the first two studies \cite{Tigik2016b,Tigik2017a} have shown a
promising perspective.

@@

\section{Collisional damping rates for plasma waves}
\label{coll-damp}
In this first analysis, we have numerically integrated Eqs. \eqref{gammaL}
for $L$ waves, and \eqref{gammaS} for $S$ waves, considering Maxwellian
velocity distribution function for the particles, without including the
new effects in the time evolution subroutine. The main objective here
was to comprehend important aspects of this so-far unknown expression,
how it relates to other equivalent plasma processes and with the
heuristic Spitzer formula, for collisional damping. The main question
was: ``Are they equivalent?'', more specifically, ``Are their intensities,
at least, in the same order of magnitude?''. The answer was no. We found
out that the Spitzer formula overestimates the collisional damping effect
in several orders of magnitude in comparison with the new expression.
Further, the insignificance of the collisional damping became even more
evident when we compared its damping rate with the collisionless (Landau)
damping rate in the same figure.

@@

\chapter{Final remarks}
\label{cha:final}
In this thesis, we have presented the results of the first analysis of a new
theory, depicted in \Cref{noneigenmode}, which combines collective processes
(eigenmodes) and collisional interactions (noneigenmodes), for Langmuir and
ion-sound waves, without any \emph{ad hoc} addition. The importance of this
formalism, became clear right in the first study, presented in \Cref{coll-damp},
where it was shown that the collisional damping rate calculated with the heuristic
Spitzer formula, that is independent of the wave-number, is highly overestimated
when compared with the rigorous expression, which has to be integrated in the
wave-number space. The Spitzer approximation is largely applied to the modeling
and interpretation of several solar phenomena observed by space-probes \cite{
  Vinas2000,Hannah2009,ZVST11,KRB12,KF13,Reid2014,Reid2015}, a fact that
emphasizes the necessity of the development of a mathematically rigorous
theory able to describe hybrid situations involving collective oscillations
and collisional interactions.

@@

\begin{appendix}
\chapter{Improved approximation for the second order susceptibility}
\label{appA}
\setcounter{equation}{0}
\renewcommand{\theequation}{A\arabic{equation}}
In this appendix, we present two different approximations applied to the
second-order susceptibility in the electrostatic bremsstrahlung equation
for Langmuir waves. Initially, for comparison, we show the original
simplification used in Ref.~\cite{YZKS16}. In the sequence, we introduce
an improved approximation for the same expression, highlighting the main
differences. This new version, though, is only suitable for fast-waves,
which is the case of Langmuir oscillations, but the same does not apply
to ion-sound waves. Moreover, the results for ion-sound waves are quite
well behaved with the original approximation, which is the same that was
initially used for  $L$ waves. Therefore, $S$ waves will take part only in
\Cref{sec:orig-appr}, while \Cref{sec:alt-approx} will be directed solely
the $L$ waves expression.

@@

Simplifying, and writing the coefficient in front of the expression in a
different way,
\begin{equation}
\begin{split}
\chi_a^{(2)}&[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
\simeq-i\frac{e_a}{T_a}\frac{\omega_{pa}^2}{k k'|{\bf k-k'}|}\frac{1}{v_{a}^2}\\
&\times\int d{\bf v''}\,\left\{\frac{T_a}{m_a}
\frac{{\bf k'}\cdot({\bf k-k'})}{{\bf k}\cdot{\bf v''}}
\left[\frac{1}{({\bf k-k'})\cdot{\bf v''}} 
  +\frac{1}{({\bf k'})\cdot{\bf v''}}\right]
+\underbrace{ \frac{\bf k'\cdot v''}{\bf k\cdot v''} 
+ \frac{({\bf k}-{\bf k'}){\bf \cdot v''}}{\bf k\cdot v''}}_{=1}
\right\} F_a({\bf v''}) + i\,{\rm Im}\chi^{(2)}
\end{split}
\end{equation}
where we have used $f_a= \hat{n} F_a$.

%%% Falta algo aqui, ver isso %%%
% \begin{equation}
% \chi_a^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
% \simeq-i\frac{e_a}{T_a}\frac{\omega_{pa}^2}{k k'|{\bf k-k'}|}\frac{1}{v_{a}^2}
% \int d{\bf v''}\,\left[\frac{T_a}{m_a}
% \frac{{\bf k'}\cdot({\bf k-k'})}{{\bf k}\cdot{\bf v''}}
% \frac{{\bf k}\cdot {\bf v''}}{({\bf k-k'})\cdot{\bf v''}}+1
% \right] F_a({\bf v''}) 
% \end{equation}
\begin{equation}
\chi_a^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
\simeq-i\frac{e_a}{T_a}\frac{\omega_{pa}^2}{k k'|{\bf k-k'}|}\frac{1}{v_{a}^2}
\int d{\bf v''}\,\left[\frac{T_a}{m_a}
\frac{{\bf k'}\cdot({\bf k-k'})}{({\bf k-k'})\cdot{\bf v''}}+1
\right] F_a({\bf v''}) 
\end{equation}

@@

Since this approximation assumes that the dominant frequency range on
the denominators is given by the dispersion relation of Langmuir waves
(see Eq. \eqref{dom-freq}), which are high frequency oscillations
near the electron plasma frequency, it is not suitable for use on
the bremsstrahlung expression for $S$ waves.

>>>>

In the context of plasma kinetic theory, processes involving waves
and kinetic instabilities, the so-called \emph{collective processes},
are almost exclusively associated with situations in which the effects
of collisional dissipation can be neglected, what happens when the
studied phenomenon evolves in a much shorter time-scale than the
collisional relaxation time of the plasma in question \cite{akhi1967}.
In such cases, the plasma dynamics may be described by the Vlasov-Maxwell
system, a complex set of coupled equations whose
%which 
% LFZ190822: Posso estar enganado, mas me parece que aqui seria mesmo
% "whose", como estava antes, e não "which".
% Sabrina: resolvi colocar "whose" de novo depois de uma rápida, mas
% controversa, pesquisa no google
solution invariably will
depend on some degree of approximation. In the presence of small
amplitude oscillations in a fully ionized plasma, we can make use
of perturbation theory in order to solve such complicated system
\cite{klimo}. From this method, one may obtain simpler approximations
like the linear theory and the quasilinear formalism, and also
more complex formulations, like the weak turbulence theory, which
takes into account low-order nonlinearities on the plasma dynamics.

@@

In the quasilinear theory, low-order nonlinear terms are kept in
the equation for the time evolution of the velocity distribution
function. The velocity distribution will then evolve in time through
a process of diffusion in velocity space, in which the diffusion
coefficient depends on the spectral energy density of the waves.
The dispersion relation is formally given by the same expression
obtained under the linear theory, except that now it depends on a
time-dependent velocity distribution function, which must vary in a
much slower time-scale than the period of the plasma oscillations.
Under such condition, the gradual changing on the velocity space
shape slowly modifies the shape of the wave spectrum, whose
% LFZ190822: Não seria mesmo "whose"?
% Sabrina: ok
new form will alter the velocity distribution function and so
on, until a new quasi-stationary equilibrium state is attained
\cite{gurnett2017}. However, depending on the phenomenon being
described this saturation state reached under the quasilinear
approximation might keep on evolving if higher order nonlinearities are taken into account
\cite{akhi2}. This kind of nonlinear analysis is given by the
\emph{weak turbulence theory}, which is the next step in this chain
of perturbative approximations.

@@

The main subject of this thesis is discussed in \Cref{noneigenmode}. In
\Cref{sec:inc-non} we show the methodology used in the formulation of this
new generalization and the outcome of its inclusion in the quasilinear
wave equation, and in the particle kinetic equation. \Cref{sec:non-non}
describes the inclusion of the noneigenmode fluctuations in the nonlinear
wave equations and the resulting terms, which are the main concern of
the present analysis. In \Cref{main}, we contextualize the present work
regarding the theory discussed in the previous chapter and present the
results obtained in appended papers. \Cref{cha:final}, summarizes the
results and discuss some remarking conclusions obtained in this analysis.
At the end of this chapter, we also deliberate the perspectives for this
new generalized formalism and its relevance for the next generation of
solar physics research.
% LFZ190822: Suponho que aqui devia ser "... a brief discussion on the
% conclusions obtained and on the perspectives ..." ?
% Sabrina: Melhorou?
% and its relevance for the next generation of solar physics research are
% also deliberated.

@@

On the left-hand side of  Eq. \eqref{eq-cin-par} we have retained the
slow adiabatic derivative $i(\partial/\partial t)$. To deal with
that we employ two-step approximation \cite{Yoon00} and redefine
the angular frequency $\omega \rightarrow \omega+i \partial/\partial t$.
Then the equation for the
% LFZ180216: "the perturbed"?
% Sabrina: OK
perturbed distribution may be iteratively
solved up to third order in electric field.  The solution is then
inserted into Eq. \eqref{poisson-flut}
% the perturbed Poisson equation
% LFZ180216: Se o nome Poisson foi mudado anteriormente, deve ser mudado aqui
% também.
% Sabrina: coloquei o número da equação no lugar. Pode ser?
% LFZ180220: OK
and,  under the assumption that there are random phases associated with
the fluctuations, we take the appropriated ensembles averages. This
procedure results in the nonlinear spectral balance equation. At this
point, according to the two-time approximation, the slow time derivative
is reintroduced \cite{YZKS16}. We then obtain the nonlinear
% LFZ190822: Seria melhor evitar a repetição de "This procedure results".
% Quem sabe aqui se escreve algo como "We then obtain the nonlinear
% spectral balance equation\footnote{..." ?
% Sabrina: Sim! Eu nem tinha percebido isso
spectral balance equation\footnote{Equation \eqref{nlebe} is not in the
  same form that appears in Refs. \cite{Yoon00,Tigik2015}. The reason
  for this choice (see Eq. 2.59 of Ref. \cite{YZKS16}), will become
  clear in the next chapter.}
  &&\frac{i}{2}\frac{\partial \epsilon({\bf k},\omega)}{\partial \omega}
  \frac{\partial \left<\delta E^2\right>_{{\bf k},\omega}}{\partial t}
  +\mbox{Re}\,\epsilon({\bf k},\omega)\left<\delta E^2 \right>_{{\bf k},\omega}
+i\mbox{Im}\,\epsilon({\bf k},\omega)\left<\delta E^2 \right>_{{\bf k},\omega}
  &&\qquad \qquad \qquad -\frac{2}{\pi}\frac{1}{k^2\epsilon^*({\bf k},\omega)}
     \sum_ae_a^2\int d{\bf v}\,\delta(\omega-{\bf k\cdot v})F_a({\bf v})
  &&=-2\int d{\bf k'} \int d\omega '\
  \biggl[\frac{\left<\delta E^2\right>_{{\bf k-k'},\omega-\omega '}}
  &&+\frac{\left<\delta E^2\right>_{{\bf k'},\omega '}}
      \left<\delta E^2\right>_{{\bf k'},\omega'}\biggr\}
  \left<\delta E^2\right>_{{\bf k},\omega}\nonumber\\
  &&+2\int d{\bf k'} \int d\omega '
\left<\delta E^2\right>_{{\bf k'},\omega '}
     \left<\delta E^2\right>_{{\bf k-k'},\omega-\omega '}
  \label{nlebe}\\
&&-\frac{4}{\pi}\int d{\bf k '} \int d\omega '\
\biggl[ \frac{[\chi^{(2)}({\bf k'},\omega '|{\bf k-k'},\omega-\omega ')]^2}
{\epsilon({\bf k-k'},\omega-\omega ')}
    \left<\delta E^2 \right>_{{\bf k},\omega}
&&-\frac{|\chi^{(2)}({\bf k'},\omega '|{\bf k-k'},\omega-\omega ')|^2}
\left<\delta E^2 \right>_{{\bf k-k'},\omega-\omega '}\biggr]
\sum_ae_a^2\int d{\bf v}\, \delta(\omega '-{\bf k \cdot v})F_a({\bf v})
&&-\frac{4}{\pi}\int d{\bf k '} \int d\omega '\
\biggl[ \frac{[\chi^{(2)}({\bf k'},\omega '|{\bf k-k'},\omega-\omega ')]^2}
{\epsilon({\bf k'},\omega ')}\left<\delta E^2 \right>_{{\bf k},\omega}
&&-\frac{|\chi^{(2)}({\bf k'},\omega '|{\bf k-k'},\omega-\omega ')|^2}
\left<\delta E^2 \right>_{{\bf k'},\omega '}\biggr]
\sum_ae_a^2\int d{\bf v}\, \delta(\omega-\omega '-{\bf (k-k')\cdot v})F_a({\bf v})
where on the left-hand side we have the expressions that correspond
to the linear equation and on the right-hand side are the nonlinear
expressions. The term
\epsilon({\bf k},\omega)=1+\sum_a\chi_a({\bf k},\omega)
is the linear dielectric response function.

@@

Equation \eqref{nlebe} is a general expression. The usual
approach in plasma kinetic theory is to assume $|\mbox{Im}\
\epsilon({\bf k},\omega)|\ll|\mbox{Re}\ \epsilon({\bf k},\omega)|$.
Then, the imaginary part of \eqref{nlebe} leads to the wave kinetic
equation, while the real part leads to the wave dispersion equation,
whose solutions 
% LFZ190822: Não seria "whose solutions", como estava antes?
%Sabrina: ok
are the wave dispersion relations.

@@

The following approximations and definitions were used to write
the above equations
\begin{displaymath}
\frac{1}{\epsilon '_\parallel({\bf k},\sigma\omega_{\bf k}^L)}
=\frac{\sigma\mu_{\bf k}^L\,\omega_{\bf k}^L}{2},\qquad
\frac{1}{\epsilon '_\parallel({\bf k},\sigma\omega_{\bf k}^S)}
=\frac{\sigma\mu_{\bf k}^S\,\omega_{\bf k}^L}{2},\qquad
\end{displaymath}
\begin{displaymath}
\mu_{\bf k}^L=1,\qquad
\mu_{\bf k}^S=|k|^3\lambda_{De}^3\biggl(\frac{m_e}{m_i}\biggr)^{1/2}
\biggl(1+\frac{3T_i}{T_e}\biggr)^{1/2}.
\end{displaymath}
% LFZ190822: Ao final da expressão acima havia um ponto "." e corrigistes
% colocando uma vírgula. Mas acho que era para ser ponto mesmo, pois a frase
% acaba ali.
% Sabrina: ok
\chapter{Weak turbulence for collisional plasmas}
\label{noneigenmode}
In \Cref{cha:weak-turb} we made a brief review of the standard weak
turbulence theory procedure. Such procedure takes into account only
the contributions from the linear eigenmodes. The basic premise of this
conventional approach claims that only frequencies $\omega=\omega_{\bf k}$
that satisfy the dispersion relations are considered significant, even if
the general electrostatic fluctuations $\left<\delta E^2\right>_{{\bf k},\omega}$
are characterized by all ${\bf k}$ and $\omega$. Therefore, the fluctuations
with 
% LFZ190822: Acho que aqui seria "with", não ''which" (i.e., "the fluctuations 
% with $\omega\ne\omega_{\bf k}$, which characterize the ...")
% Sabrina: de fato.
$\omega \ne \omega_{\bf k}$, which characterize the noneigenmodes,
are ignored. In Ref. \cite{YZKS16} the authors present a generalization
of this customary approach, where, besides the traditional inclusion of
the normal modes, it is also taken into account the contribution from the
noneigenmode fluctuations. The result is a generalized expression for the
spectral energy density of the waves, with some remarkable consequences
for the wave and particle kinetic equations.

The generalized spectral energy density, which contains the noneigenmode
contribution, is the central factor of this new kinetic turbulence theory
for collisional plasmas. When it is substituted in the nonlinear terms of
the nonlinear spectral balance equation, three new terms appear in the wave
kinetic equation. The first expression is an extension for the spontaneous
scattering equation. The second term is a new, rigorous expression for the
collisional damping rate of plasma waves. The third equation depicts a
hitherto unknown process of electrostatic radiation emission, in the eigenmode
frequency range, due to particle scattering. This underlying electrostatic
form of braking radiation was
% LFZ190822: Esse "then" me parece desnecessário.
% Sabrina: ok
called \emph{electrostatic bremsstrahlung}
\cite{YZKS16}. For the particle kinetic equation, the application of this
generalized expression is responsible for the arising of the Balescu-Lenard
collision integral, without any \emph{ad hoc} addition.

@@

\section{Noneigenmode contribution to nonlinear wave
  kinetic equation}
\label{sec:non-non}
For the nonlinear wave kinetic equation, the implementation is far more
extensive and complicated than the two previous cases. In this text, we
provide a brief explanation of the method, which is not very different
from the quasilinear case, though it is way more complex, and present some
critical remarks regarding the inclusion of noneigenmodes in the nonlinear
wave equation. It is worth to mention again, that a more detailed description
of the procedure
% LFZ190822: Talvez fique melhor "... a more detailed description of the
% procedures for inclusion of the ..."
% Sabrina: ok
for the inclusion of the noneigenmode contribution in the weak turbulence's
equations can be seen in \cite{YZKS16}.

@@

\chapter{Weakly turbulent processes in the presence of
  collisional interactions}
\label{main}
The generalization introduced in \cite{YZKS16} and summarized in
\Cref{noneigenmode}, is an innovative approach, in which the contribution
of the usually neglected noneigenmode fluctuations is taken into account
along with the well-known eigenmodes contribution. The outcome of this new
formulation is a first principles theory that combines both collective
and non-collective processes, assuming the propagation of electrostatic
oscillations in unmagnetized plasmas, without any \emph{ad hoc} addition.
Such theory is the basis of the present research, in which the
% LFZ190822: Não seria "whose", como estava antes?
% Sabrina: troquei para "in which"
primary objective
is performing numerical analysis of the generalized weak turbulence equations,
and then investigate its applications on the description and interpretation
of space plasma phenomena. More specifically, the solar plasma, where the
results of the first two studies \cite{Tigik2016b,Tigik2017a} have shown a
promising perspective.

@@

\section{Collisional damping rates for plasma waves}
\label{coll-damp}
In this first analysis, presented in Ref. \cite{Tigik2016b}, we have
numerically integrated Eqs. \eqref{gammaL}
% LFZ190822: O artigo está anexado, mas acho que mesmo assim vale dizer qual
% é o artigo na lista de referências. Algo como
% "In this first analysis, presented in Ref. \cite{Tigik...}, 
% we have numerically integrated Eqs. \eqref{gammaL} for ..."
% Sabrina: ok
for $L$ waves, and \eqref{gammaS} for $S$ waves, considering Maxwellian
velocity distribution function for the particles, without including the
new effects in the time evolution subroutine. The main objective here
was to comprehend important aspects of this so-far unknown expression,
how it relates to other equivalent plasma processes and with the
heuristic Spitzer formula, for collisional damping. The main question
was: ``Are they equivalent?'', more specifically, ``Are their intensities,
at least, in the same order of magnitude?''. The answer was no. We found
out that the Spitzer formula overestimates the collisional damping effect
in several orders of magnitude in comparison with the new expression.
Further, the insignificance of the collisional damping became even more
evident when we compared its damping rate with the collisionless (Landau)
damping rate in the same figure.

@@

\chapter{Final remarks}
\label{cha:final}
In this thesis, we have presented the results of the first analyses 
% LFZ190822: Talvez seja mais correto dizer "of the first analyses ...", que
% é plural, enquanto que "analysis" é singular.
% Sabrina: ok
of a new
theory, depicted in \Cref{noneigenmode}, which combines collective processes
(eigenmodes) and collisional interactions (noneigenmodes), for Langmuir and
ion-sound waves, without any \emph{ad hoc} addition. The importance of this
formalism, became clear right in the first study, presented in \Cref{coll-damp},
where it was shown that the collisional damping rate calculated with the heuristic
Spitzer formula, that is independent of the wave-number, is highly overestimated
when compared with the rigorous expression, which has to be integrated in the
wave-number space. The Spitzer approximation is largely applied to the modeling
and interpretation of several solar phenomena observed by space-probes \cite{
  Vinas2000,Hannah2009,ZVST11,KRB12,KF13,Reid2014,Reid2015}, a fact that
emphasizes the necessity of the development of a mathematically rigorous
theory able to describe hybrid situations involving collective oscillations
and collisional interactions.

@@

\begin{appendix}
\chapter{Improved approximation for the second order susceptibility}
\label{appA}
\setcounter{equation}{0}
\renewcommand{\theequation}{A\arabic{equation}}
In this appendix, we present two different approximations applied to the
second-order susceptibility in the electrostatic bremsstrahlung equation
for Langmuir waves. Initially, for comparison, we show the original
simplification used in Ref.~\cite{YZKS16}. In the sequence, we introduce
an improved approximation for the same expression, highlighting the main
differences. This new version, though, is only suitable for fast-waves,
which is the case of Langmuir oscillations, but does not apply to the case
% LFZ190822: Aqui me parece que ficaria melhor dizer This new version, though,
% is only suitable for fast waves, which is the case of Langmuir oscillations,
% but does not apply to the case of ion-sound waves. does not apply
% Sabrina: ok
of ion-sound waves. Moreover, the results for ion-sound waves are quite
well behaved with the original approximation, which is the same that was
initially used for $L$ waves in Ref.~\cite{YZKS16}.
% LFZ190822: Acho que aqui cabe continuar dizendo "... for $L$ waves in
% Ref.~\cite{YZKS16}."
% Sabrina: ok
Therefore, $S$ waves will be considered only in
% LFZ190822: Acho melhor "will be considered", em vez de "will take part"
\Cref{sec:orig-appr}, while \Cref{sec:alt-approx} will be directed solely
% LFZ190822: Sugiro "... will be directed solely to the use in expressions
% related to $L$ waves.", em lugar de "the $L$ waves expression."
% Sabrina: acho que se eu usar "expressions" vai dar a impressão de que
% essa aproximação vai ser usada em outra equação que não seja a do
% electrostatic bremsstrahlung. Não lembro se a gente chegou a usar essa
% aproximação na expressão do amortecimento colisional. Mas acho que não.
to the  expression for $L$ waves.

@@

Simplifying, and writing the coefficient in front of the expression in a
different way,
\begin{equation}
\begin{split}
\chi_a^{(2)}[{\bf k'},&{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
\simeq-i\frac{e_a}{T_a}\frac{\omega_{pa}^2}{k k'|{\bf k-k'}|}\frac{1}{v_{a}^2}\\
&\times\int d{\bf v''}\,\biggl\{\frac{T_a}{m_a}
\frac{{\bf k'}\cdot({\bf k-k'})}{{\bf k}\cdot{\bf v''}}
\left[\frac{1}{({\bf k-k'})\cdot{\bf v''}}
+\frac{1}{({\bf k'})\cdot{\bf v''}}\right]\\
&+\underbrace{ \frac{\bf k'\cdot v''}{\bf k\cdot v''} 
+ \frac{({\bf k}-{\bf k'}){\bf \cdot v''}}{\bf k\cdot v''}}_{=1}
\biggr\} F_a({\bf v''}) + i\,{\rm Im}\chi^{(2)},
\end{split}
\end{equation}
\begin{equation}
  \begin{split}
\chi_a^{(2)}[{\bf k'},&{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
\simeq-i\frac{e_a}{T_a}\frac{\omega_{pa}^2}{k k'|{\bf k-k'}|}\frac{1}{v_{a}^2}\\
&\times\int d{\bf v''}\,\left[\frac{T_a}{m_a}
\frac{{\bf k'}\cdot({\bf k-k'})}{({\bf k-k'})\cdot{\bf v''}}+1
\right] F_a({\bf v''})
\end{split}
\end{equation}
where we have used $f_a= \hat{n} F_a$.

@@

Since this approximation assumes that the dominant frequency range on
the denominators is given by the dispersion relation of Langmuir waves
(see Eq. \eqref{dom-freq}), which are high frequency oscillations
near the electron plasma frequency, it is not suitable for use in
% LFZ190822: "on", ou "in"?
% Sabrina: ok
the bremsstrahlung expression for $S$ waves.
